\documentclass[preprint2]{aastex}
\usepackage{natbib}
\bibliographystyle{apj}

\newcommand{\mhd}{magnetohydrodynamic}

\shorttitle{Coronal Seismology}
\shortauthors{Farris}

\begin{document}

\title{Coronal Seismology}
\author{Laurel Farris}
\affil{New Mexico State University}
\email{laurel@laurelfarris.com}

\begin{abstract}
Coronal seismology involves the investigation of \mhd (MHD) wave and
ocillatory phenomenae that arise in the solar corona. Here some of the
dominant waves, oscillations, and modes are intimately investigated in
the literature. Analysis of data from the Atmospheric Imaging
Assembly (AIA) instrument on the Solar Dynamics Observatory (SDO) is
also presented, both as stand-alone research and in the broader
context of coronal seismology. 
\end{abstract}
\keywords{Sun: corona - Sun: oscillations - Sun: seismology}

\section{Introduction}\label{intro}
Here is some stuff about coronal seismology.

In \S\ref{MHD}, several major types of waves and oscillatory modes in
the solar corona are described, along with recent investigations into
each one. \S\ref{data} includes a description of a research project and
its implications for the broader field of coronal seismology in
\S\ref{analysis}. Conclusions and future work are summed up in
\S\ref{conclusion}.

\section{Magnetohydrodynamic Waves}\label{MHD}

\subsection{Kink Oscillations}
Kink oscillations are commonly associated with coronal loops, and
characterize the spacial oscillations that occur over the surface of
the loop (\cite{Nak}).


%While temporal variations have been observed for the past (?) years
%or so, spatial variations were not revealed until the launch of
%TRACE, which provided sufficient spatial resolution to distinguish
%the spatial displacements of MHD oscillations.
% or
%the different characteristics of MHD oscillations.
Some of the first observations of these spatial variations
were carried out by~\cite{kink_1},
who utilized some of the first data released from the TRACE mission in
order to investigate the oscillations present in coronal loops.
~\cite{kink_2} investigated the distributions of the damping
of kink oscillations.

\subsection{Sausage Oscillations}


\section{Data}\label{data}
As part of the general topic of coronal seismology,
a small research project was carried out as well, continuing
over from several semesters previously.

\section{Analysis}\label{analysis}

\section{Conclusion}\label{conclusion}
And we're finished.

\bibliography{reffile}
\end{document}
